Motivation

### 2017-07-19 Reports/USAID.tex
secciones numeradas en Rmd
posili
Do files updated for pilot 3

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

A. Logistic Regression

B. Probit

C. Random Forest (100 trees)

D. Single-hidden-layer Neural Network (20 nodes in the hidden layer and
10\% weight decay)

E. Gradient Boosting

Due to our sample size, all hyperparameters were chosen specifically to
avoid overfitting. Models were chosen for each outcome based on
classification accuracy for the test set.

XXX

@@

A. OLS regression

B. GLM Boosting

C. Random Forest (100 trees)

D. Ridge Regression

The 7 models to be used in the calculator were chosen based on the
\emph{MAPD (Mean Absolute Percentage Deviation).} This evaluation
measure was chosen because we had no zero values in our dependent
variables and were inclined to giving rather conservative predictions to
parties.

XXXXX

@@

\begin{figure}[htbp]
\centering
\includegraphics{../Paper/Figuras/calctreat.png}
\caption{Calculator predictions in the first pilot}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Given a case ending in a court ruling, how likely is to recover a
  positive compensation?
\item
  What would be that expected compensation?
\item
  Given a case ending in settlement, what would be the expected
  compensation? \#\# Data
\end{enumerate}

@@

Our classification problem became slightly different. In order to assess
the unbalancedness of our court rulings sample -only 24\% of court
rulings ever recover something- we used a Synthetic Minority
Over-Sampling Technique -see
\href{http://jair.org/media/953/live-953-2037-jair.pdf}{(Chawla et.al.,
2002)} for more detail- and did a 80-20 train vs.~test split on our
data.

@@

The final models were chosen based on the Mean Squared Error, and
certain aspects of the out-of-sample error distributions. For this
second criterion we estimated this distribution by retraining the model
1000 times on a 70-30 train-test split and computing prediction errors.

\textbf{XXX (3)} ** Aquí tenemos las grafiquitas de las distribuciones
de errores con las que evaluamos los modelos (les anexo el doc, por si
no lo recuerdan). Puedo poner esas, aunque no me encantan, puedo poner
una tablita con los MSE, puedo hacer otras\ldots{} Como me digan**

@@

\textbf{XXX Este me falta}

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
%\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{float}
\usepackage[labelfont=bf]{caption}
\usepackage[labelfont=bf, justification=justified]{subcaption}
\captionsetup{position=top}
\captionsetup[subfigure]{justification=centering}

\graphicspath{{./Figuras/}}
\usepackage{epstopdf}
\epstopdfDeclareGraphicsRule{.tiff}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tiff}

@@

\begin{itemize}
\item Logistic Regression

\item Probit

\item Random Forest (100 trees)

\item Single-hidden-layer Neural Network (20 nodes in the hidden layer and 10\% weight decay)

\item Gradient Boosting
\end{itemize}

Due to our sample size, all hyperparameters were chosen specifically to
avoid overfitting. Models were chosen for each outcome based on
classification accuracy for the test set. Figure \ref{accuracy_scores} shows the classification accuracy rates of all our final discrete models.

\begin{figure}[H]
   \caption{Accuracy scores by binary outcome}
   \label{accuracy_scores}
    \begin{center}
    \includegraphics[width=0.3\textwidth]{oos_fit_categorical.tiff}
    \end{center}
\end{figure}

@@

\begin{itemize}
\item OLS regression

\item GLM Boosting

\item Random Forest (100 trees)

\item Ridge Regression
\end{itemize}

The 7 models to be used in the calculator were chosen based on the \emph{MAPD (Mean Absolute Percentage Deviation).} This evaluation
measure was chosen because we had no zero values in our dependent
variables and were inclined to giving rather conservative predictions to
parties. Figures \ref{duration_predictions} and \ref{compensation_predictions} show the out-of-sample fit for every final continuous model. For each model, we regress the prediction on our dependent variable and show the $R^2$ in the plot subtitle.

\begin{figure}[H]
    \caption{Duration predictions}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        %{\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
\end{figure}

\begin{figure}[H]
    \caption{Compensation predictions}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{Calculator predictions in the first pilot}
\includegraphics{calctreat.png}
\end{figure}

\pagebreak

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Given a case ending in a court ruling, how likely is to recover a
  positive compensation?
\item
  What would be that expected compensation?
\item
  Given a case ending in settlement, what would be the expected
  compensation?
\end{enumerate}

\subsection{Data}\label{data-1}

@@

Our classification problem became slightly different. In order to assess
the unbalancedness of our court rulings sample -only 24\% of court
rulings ever recover something- we used a Synthetic Minority
Over-Sampling Technique (see
\href{http://jair.org/media/953/live-953-2037-jair.pdf}{Chawla et.al., 2002}) and did a 80-20 train vs.~test split on our
data.

@@

The final models were chosen based on the Mean Squared Error, and
certain aspects of the out-of-sample error distributions. For this
second criterion we estimated this distribution by retraining the model
1000 times on a 70-30 train-test split and computing prediction errors. Figure \ref{continuous_predictions}

\begin{figure}[H]
    \caption{Compensation predictions}
    \label{continuous_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_laudo.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{Information sheet for plaintiff}
\includegraphics[width=.75\textwidth]{calctreat_act.pdf}

\end{figure}

\begin{figure}[H]
\centering
\caption{Information sheet for defendant}
\includegraphics[width=.75\textwidth]{calctreat_dem.pdf}

\end{figure}
